A neural coarse graining theory of consciousness/\newline Non-trivial Informational closure through neural coarse-graining as the Fundamental Informational Correlates of Consciousness

### 2019-04-25 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

		\subsection{Unconscious Processing}
		As described above, if information processing fails to meet either one of the two necessary conditions, information remains unconscious. First, considering processes which fail to meet the first condition. That is, a information process is not NTIC. We can see many information processing in the neural network system fall in this category.

		\begin{equation}\label{eq:InformationFlow}
		\begin{aligned}
            P(A|S)
        \end{aligned}
		\end{equation}

>>>>

		\subsection{Unconscious Processing}
		\begin{ants}
		    @ As described above, if information processing fails to meet either one of the two necessary conditions, information remains unconscious.

		    @ First, considering processes which fail to meet the first condition. That is, a information process is not NTIC. We can see many processes in the neural network system fall in this category.

		    @ In this category, processes cannot form NTIC. The internal states of the processes are partially or fully determined by environment states, i.e. information is not closed. Reflective behaviours are one of the main subcategory.

		    @Reflective behaviours usually are considered as automatic and non-conscious behavioural controls. \citep{casali2013theoretically}\needref{More referene}.

		    @ In modern reinforcement learning framework, this usually is referred to policy-based agents. The agents constructs a policy function that maps sensory inputs to the action space \citep{sutton2018reinforcement}.

		    @  Roughly speaking, a policy is a mapping from perceived states of the environment to actions to be taken when in those states. It corresponds to what in psychology would be called a set of stimulus–response rules or associations

		    @ The same principle can be applied to blindsight and procedure memory which are often considered as the classical cases of unconscious processing

		    @ This classic patient study of D.F. who has apperceptive agnosia \citep{10.3389/fneur.2014.00255} also falls in this category. With online sensory inputs, the neural system can create functional processes without forming NTIC.

		    @ Note that, when we prolong the temporal interval between stimulus and action, usually consciousness is necessary for learning associations. \needref{time}

		    @ Anoher case is that, processes are information closed but it is trivial.

		----------------------------------------------------------------------------
		=== -

		--- 
		procedure memory
		Reflective reaction, blindsight,

		\begin{equation}\label{eq:InformationFlow}
		\begin{aligned}
            \pi(A|S)\\
            {J_{t}(E \rightarrow Y )} & {:= I(Y_{t+1};E_{t}|Y_{t})} > 0
        \end{aligned}
		\end{equation}
		\needhelp{Math here}

		\begin{figure}
			\includegraphicsTodo[width=0.8\textwidth]{WritingMaterials/S_Y_A/S_Y_A_01.png}
			\caption{Policy network}
			\label{fig:s2a}
		\end{figure}
